%%==================================================
%% thanks.tex for SJTU Bachelor Thesis
%% version: 0.5.2
%% Encoding: UTF-8
%%==================================================

\begin{thanks}

Here, I sincerely express my gratitude to all those who have ever helped me to accomplish this topic during my last few months in Shanghai Jiao Tong University. The selfless and enthusiasim of them really helps a lot in my algorithm designing part and my evalution part. 

Firstly, I have to appreciate my supervisor, Professor Xiaofeng Gao, for her valuable advices and selfless assistance in the whole process. From the beginning stage, she gave me many suggestions on my topic, and taught me how to make innovations in this area. She also led me to the world of doing rigorous researches. With her help, I learnt how to establish a model and analyse its complexity. I also learnt how to design acceptable and practical algorithms and test them by doing simulation. It was her that guided me a lot in this world of computer network, and gave me confidence to proceed my topic on OpenFlow. She is the most important person for me to finish my graduation project.

Then, I am very thankful to Mr. Wanchao Liang, who is a pioneer in the area of load balancing in DCN in our lab. It was based on his previous work that I further my research. He also instructed me how to do in some key stage. Without his effort, I would not be able to perfect the load balancing schemes in OpenFlow. I appreciate it a lot for his assistance in establishing the model, and I wish him a bright future.

Finally, I would send my thanks to Professor Guihai Chen and all my friends and schoolmates who have taken effort on this draft. Some of them helps me make a lot progress in the evaluation part, and some of them cheers me up when I confront difficulties in this project. Thanks for my classmates in the IEEE class, who inspire me to take actions to improve myself. And also thanks for ANL for the environent it provided for all these two years, which improves my ability during my undergraduate days.

\end{thanks}

